---
title: "User's guide"
output: html_fragment
---
### Protein and mRNA data import 
Import of protein and mRNA data can be done in 2 separate files or in a single *xlsx* file. Multiple formats (tab-separated, comma-separated, ...) are supported in the use of separate files. *xlsx* file must include both data tables in different named tabs. User can switch between these 2 import methods by clicking on the *Single file* checkbox.    
Protein and mRNA data must have their identifiers as row names and a column of mRNA or protein identifiers associated to the corresponding protein and MRNAs, respectively. 

``` {r include=FALSE}
library(knitr)
library(readxl)
source("global.r")
data_exp_mrna<-read_xlsx("../data_kiwi/test.xlsx",sheet = "Transcrits")
data_exp_prot<-read_xlsx("../data_kiwi/test.xlsx",sheet = "Proteines")
data_exp<-loadData("../data_kiwi/test.xlsx","Transcrits","Proteines",F)
data_mrna<-data_exp$mrna
data_prot<-data_exp$prot

```
``` {r results='asis',echo=FALSE}
colnames(data_exp_mrna)[1]<-""
colnames(data_exp_prot)[1]<-""
kable(data_exp_mrna[,1:8],caption="Extract of a mRNA data raw table")
kable(data_exp_prot[,1:8],caption = "Extract of a protein data raw table")
```
It is necessary to have the developmental stages and their samples as column names in the protein table. Samples of a same time stage can be defined 
### Weight data import and fitting 

### Calculation of ks and kd 
